Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-29 paper/reply.tex
reply to reviewer 3

@@

>>>>

\subsection*{Reviewer \#3 comments followed by the authors' answers:}
\begin{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We have evaluated our approach using standard benchmarks taken from the control literature [3,15,21,22,35]. Larger benchmarks would strengthen our claims; however, related work on controller synthesis typically considers even smaller benchmarks (cf. 3.5 and and 4.1). As far as we know, the CEGIS approach that addresses FWL uncertainties in digital controllers has not been described or evaluated in the literature.}
\end{quote}
